---
title: "Assignment 1"
author: "Dave Miller"
date: "1/30/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

**Due date: ** Wednesday, 2/6/19 at 11:59pm.
\vspace{.5in}

1. Choose a data source from the preloaded data sources in R for a **regression problem**:

$$Y \sim f(X),$$
where $Y$ is your response variable, and $X$ is your indicator.  Present your answer as follows:

- **Data Source :**
- **Y :**
- **X :**

and print the first 6 rows of your data.
```{r echo=TRUE}

```


\vspace{.2in}

2. Plot your data using ggplot with colored dots (not black) and a theme of your choosing (not the default theme).  Be sure to add a title to the plot.

```{r echo=TRUE}

```


\vspace{.2in}


3. Split your dataset into training and testing sets using a 75% / 25% train / test split ratio.

```{r echo=TRUE}

```


\vspace{.2in}


4. Use the built in `lm()` function to build a **linear model** on the training set only and present the coefficients to the model.

```{r echo=TRUE}

```


\vspace{.2in}


5. Find the MSE of the linear model on both the training and test set. 

```{r echo=TRUE}

```


\vspace{.2in}


6. Repeat problems 4-5 for polynomials of degree 2-10.  

```{r echo=TRUE}

```


\vspace{.2in}


7. Is there a model you found in problem 6. that has **overfit** the training data?  Explain your reasoning.

\vspace{.2in}

8. Use your work from problems 4-6 to determine the model that is best to use on the dataset.  Explain your reasoning on why you chose this model in detail, stating specfic values computed in problems 5-6.

